---
title: "PS5-Xbox sentiment analysis"
author: "Amos Anzele"
date: "12/3/2020"
output:
  html_document: default
  pdf_document: default
---


  Boasting 2 billion monthly active users, YouTube us the second highest visited sire with 2 billion active monthly users.  At 335 million monthly active users, Twitter is also one of the most used social networking platforms in the world.  With the release of the Playstation 5 and Xbox series X, I wanted to leverage the interactions from both these platforms to understand the reception each console is getting.  From my the people I interact with, the Playstation console always seems to have the most favorable reviews compared the Xbox.

[Link to my Github for datasets](https://github.com/aanzele/PS5_project)

Required packages: 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, TRUE,fig.width=12, fig.height=8)
library(tidyverse)
library(tidytext)
library(lubridate)
library(textdata)
library(gridExtra)
library(wordcloud)
library(tm)
library(gdata)
library(textmineR)
library(rpart)
library(rpart.plot)
library(randomForest)
```

Data collected from Twitter and Youtube ([YouTube video comparing both products from popular YouTuber](https://www.youtube.com/watch?v=Jq-ODza3Kpc)):
```{r}

xbox_tw<- read_csv("xboxTweets.csv")

ps_tw<- read_csv("ps5Tweets.csv")

yt <- read_csv("ytcomments.csv")

```

Exploring the data:
  - Both Twitter datasets have 17 variables, while the YouTube data has 16, however the YouTube comments on this video is about three times the size.
```{r}
head(xbox_tw)

head(ps_tw)

head(yt)

dim(xbox_tw)

dim(ps_tw)

dim(yt)

names(xbox_tw)

names(ps_tw)

names(yt)
```

# 5 descriptives from the dataset

#Cleaning & seeing top words for xbox tweets

```{r}
'%!in%' <- function(x,y)!('%in%'(x,y))

#Top 20 words for Xbox tweets

xbox_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  filter(word %!in% c("https","t.co","rt","4","12","500","rangermj","person","tweet")) %>% 
  count(word,sort=TRUE) %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(y=word,x=n))+
  geom_col()+
  labs(title="Top words in Xbox tweets",
       y="",
       x="")+
  theme_light()
  

```


#Cleaning & seeing top words for PS5 tweets

```{r}
#Top 20 words for Xbox tweets

ps_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  filter(word %!in% c("https","t.co","rt","4","12","500","leanandcuisine","glock","pay5n7yiup","1000","fe0f","aint")) %>% 
  count(word,sort=TRUE) %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(y=word,x=n))+
  geom_col()+
  labs(title="Top words in PS5 tweets",
       y="",
       x="")+
  theme_light()
  
  

```


#Cleaning & seeing top words for Youtube comments

```{r}
#Top 20 words from youtube tweets


yt %>% 
  select(textOriginal) %>% 
  unnest_tokens(word,textOriginal)  %>% 
  anti_join(stop_words) %>% 
  filter(word %!in% c("https","t.co","rt","4","12","500","2")) %>% 
  count(word,sort=TRUE) %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(y=word,x=n))+
  geom_col()+
  labs(title="Top words in Xbox tweets",
       y="",
       x="")+
  theme_light()
  
  
```

# Tweets by time for Xbox
```{r}
xbox_tw %>% 
  mutate(created=floor_date(created, unit="2 minute")) %>% 
  count(created) %>% 
  ggplot(aes(x=created,y=n))+
  geom_line()+
  labs(title="Tweet trend of Xbox tweets on twitter",
       y="Count of tweets",
       x="Mention Time")+
  theme_light()
  
```



# Tweets by time for PS
```{r}
ps_tw %>% 
  mutate(created=floor_date(created, unit="2 minute")) %>% 
  count(created) %>% 
  ggplot(aes(x=created,y=n))+
  geom_line()+
  labs(title="Tweet trend of PS tweets on twitter",
       y="Count of tweets",
       x="Mention Time")+
  theme_light()
  
```


# Comparisons

#Creating sentiment analysis for xbox & PS tweets & Youtube comments 
```{r}
p1 <- xbox_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  count(sentiment) %>% 
  mutate(sentiment=fct_reorder(sentiment,n)) %>% 
  ggplot(aes(x=n,y=sentiment,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Sentiments from Xbox tweets",
       y="Sentiments",
       x="Frequency")
  
p2 <- ps_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  count(sentiment) %>% 
  mutate(sentiment=fct_reorder(sentiment,n)) %>% 
  ggplot(aes(x=n,y=sentiment,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Sentiments from PS tweets",
       y="Sentiments",
       x="Frequency")


p3 <- yt %>% 
  select(textOriginal) %>% 
  unnest_tokens(word,textOriginal)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  count(sentiment) %>% 
  mutate(sentiment=fct_reorder(sentiment,n)) %>% 
  ggplot(aes(x=n,y=sentiment,fill=sentiment))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Sentiments from Youtube comments",
       y="Sentiments",
       x="Frequency")


grid.arrange(p1,p2,p3)
```

What are the top positive words from Xbox, PS & YT tweets

```{r}
p4 <- xbox_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>%
  filter(sentiment=="positive") %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x=n,y=word,fill=word))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Top positive words - Xbox",
       y="",
       x="Frequency")
  
p5 <- ps_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>%
  filter(sentiment=="positive") %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x=n,y=word,fill=word))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Top positive words - PS",
       y="",
       x="Frequency")
  


p6 <- yt %>% 
  select(textOriginal) %>% 
  unnest_tokens(word,textOriginal)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>%
  filter(sentiment=="positive") %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x=n,y=word,fill=word))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Top positive words - Youtube",
       y="",
       x="Frequency")


grid.arrange(p4,p5,p6,nrow=1)
```


Top negative words from Xbox, PS5 & youtube comments

What are the top positive words from Xbox, PS & YT tweets

```{r}
p7 <- xbox_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>%
  filter(sentiment=="negative") %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x=n,y=word,fill=word))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Top negative words - Xbox",
       y="",
       x="Frequency")
  
p8 <- ps_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>%
  filter(sentiment=="negative") %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x=n,y=word,fill=word))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Top negative words - PS",
       y="",
       x="Frequency")
  


p9 <- yt %>% 
  select(textOriginal) %>% 
  unnest_tokens(word,textOriginal)  %>% 
  anti_join(stop_words) %>% 
  inner_join(get_sentiments("bing")) %>% 
  count(word,sentiment,sort=TRUE) %>%
  filter(sentiment=="negative") %>% 
  mutate(word=fct_reorder(word,n)) %>% 
  slice(1:20) %>% 
  ggplot(aes(x=n,y=word,fill=word))+
  geom_col(show.legend = FALSE)+
  theme_light()+
   labs(title="Top negative words- youtube",
       y="",
       x="Frequency")


grid.arrange(p7,p8,p9,nrow=1)
```

Creating wordcloud of words from Xbox, Ps & Youtube data

```{r}
xbox_topwords <- xbox_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  count(word)

ps_topwords <- ps_tw %>% 
  select(text,created) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words) %>% 
  count(word)

yt_topwords<- yt %>% 
  select(textOriginal) %>% 
  unnest_tokens(word,textOriginal)  %>% 
  anti_join(stop_words) %>% 
  count(word)

pal <- brewer.pal(8, "Dark2")

```

Word cloud for Xbox 
```{r}
xbox_topwords %>% 
  filter(word %!in% c("https","t.co","rt","4","12","500","rangermj","person")) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```


Word cloud for PS 
```{r}
ps_topwords %>% 
  filter(word %!in% c("https","t.co","rt","4","12","500","leanandcuisine","glock","pay5n7yiup","1000","fe0f","aint")) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```


Word cloud for Youtube 
```{r}
yt_topwords %>% 
  filter(word %!in% c("https","t.co","rt","4","12","500","2")) %>%
  with(wordcloud(word, n, random.order = FALSE, max.words = 50, colors=pal))
```

Topic Modeling in R

```{r}
xbox_words <- xbox_tw %>% 
  select(text) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words)

ps_words <- ps_tw %>% 
  select(text) %>% 
  unnest_tokens(word,text)  %>% 
  anti_join(stop_words)

yt_words <- yt %>% 
  select(textOriginal) %>% 
  unnest_tokens(word,textOriginal)  %>% 
  anti_join(stop_words) 


myCorpus <- Corpus(VectorSource(xbox_words$word))  
dtm <- DocumentTermMatrix(myCorpus)
dtm_new <- removeSparseTerms(dtm,sparse = 0.999)
rowTotals <- apply(dtm_new , 1, sum) #Find the sum of words in each Document
dtm.new   <- dtm_new[rowTotals> 0, ]  
topic_xbox <- topicmodels::LDA(dtm.new, k = 3, control = list(seed = 1234))


x_topic <- tidy(topic_xbox)

x_top_terms <- x_topic %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)


x <- x_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()+
  theme_light()+
  labs(title="Topics from Xbox tweets")


myCorpus_1 <- Corpus(VectorSource(ps_words$word))  
dtm_1 <- DocumentTermMatrix(myCorpus_1)
dtm_new_1 <- removeSparseTerms(dtm_1,sparse = 0.999)
rowTotals <- apply(dtm_new_1 , 1, sum) #Find the sum of words in each Document
dtm.new_1   <- dtm_new_1[rowTotals> 0, ]  
topic_ps <- topicmodels::LDA(dtm.new_1, k = 3, control = list(seed = 1234))


ps_topic <- tidy(topic_ps)

ps_top_terms <- ps_topic %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ps <- ps_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()+
  theme_light()+
  labs(title="Topics from PS tweets")

myCorpus_2 <- Corpus(VectorSource(yt_words$word))  
dtm_2 <- DocumentTermMatrix(myCorpus_2)
dtm_new_2 <- removeSparseTerms(dtm_2,sparse = 0.999)
rowTotals <- apply(dtm_new_2 , 1, sum) #Find the sum of words in each Document
dtm.new_2   <- dtm_new_2[rowTotals> 0, ]  
topic_yt <- topicmodels::LDA(dtm.new_2, k = 3, control = list(seed = 1234))


yt_topic <- tidy(topic_yt)

yt_top_terms <- yt_topic %>%
  group_by(topic) %>%
  top_n(10, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

yt <- yt_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered()+
  theme_light()+
  labs(title="Topics from YT comments")


grid.arrange(x,ps,yt)
```
**Conclusion:**  My original intent was to understand how these two products were being received, and which one garnered the most positive acclaim.  As stated above, I believed the Playstation would come out the clear favorite, but after this analysis, I come out needing to expand my datasets to get a clearer picture.  I also need to collect more data from the YouTube comments as there seems to be more engagement.   

